Plot `r paste(params$species)` responses to climate covariates to inform threshold choices for VOCC

### 2019-12-17 analysis/VOCC/3-fixed-var-response-plots.Rmd
change plotted ranges to 95% of observed

---
title: "Plot `r paste(params$species)` responses to climate covariates to inform threshold choices for VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    species: "Flathead Sole" 
    priors: FALSE # call model that used priors?
    log_temp: TRUE # should temperature be log()
    model_w_do: TRUE
    fix_depth: TRUE
    #covs: "-all-" #"-log-both-fixed-depth"
    #covs: "-past-2017"
    # fix_depth: FALSE #TRUE
    # #covs: "-log-both-noAR1" #"-log-both-fixed-depth"
    # covs: "-log-both-AR1"
    cov_number: 2 #covs: "-log-both-noOMEGA" # covariate string used to name model rds
---

@@

try({
  # loads global models with 2016 excluded due to strangely high DO 
  add2016 <- ""
  x2016 <- "x2016"
  # for models using 2016 
  # add2016 <- "-do"
  #  x2016 <- ""
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed", add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  adult<-sdmTMB:::update_model(adult) 
  imm <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed", add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm <-sdmTMB:::update_model(imm) 
  })
  try({total <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, "-fixed", add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL
if (!exists("total")) total <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey1 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey1 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  })
  try({total1 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
  })
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL
if (!exists("total1")) total1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey4 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey4 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  })
  try({total4 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL
if (!exists("total4")) total4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey16 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
   ))
   imm_survey16 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
   ))
  })
  try({total16 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult_survey16")) adult_survey16 <- NULL
if (!exists("imm_survey16")) imm_survey16 <- NULL
if (!exists("total16")) total16 <- NULL

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- paste0(x2016, covs, priors) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- exp(roots[["optimal"]])
   do[[i]]$lower_do_50 <- exp(roots[["lower_threshold"]])
   do[[i]]$upper_do_50 <- exp(roots[["upper_threshold"]])
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- exp(roots75[["lower_threshold"]])
   do[[i]]$upper_do_75 <- exp(roots75[["upper_threshold"]])
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- exp(roots25[["lower_threshold"]])
   do[[i]]$upper_do_25 <- exp(roots25[["upper_threshold"]])
   do[[i]]$x <- exp(do[[i]]$x)
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0.2, 8), x_breaks = c(1,2,3,4,5,6,7,8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=(do[[i]]$lower_do_50), linetype="longdash", alpha = 0.75) +
        #geom_vline(xintercept=(do[[i]]$upper_do_50), linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=(do[[i]]$lower_do_75), linetype="dotted", alpha = 0.5) +
        #geom_vline(xintercept=(do[[i]]$upper_do_75), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$lower_do_25), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$optimal_do), size= 1.2, colour = "darkgrey") 
        #geom_vline(xintercept=(do[[i]]$upper_do_25), linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(2, 12), x_breaks = c(3,4,5,6,7,8,9,10,11)) +
        ggtitle(paste(species, names(model_list[i]))) + 
        geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") 
  } else {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } 
 } else {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } 
}

@@

Save DO plots
```{r eval=F}
if(model_w_do) {
png(
  file = paste0("figs/", spp, "/do-", spp, x2016, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
}
```

Save temperature plots
```{r eval=F}
png(
  file = paste0("figs/", spp, "/temp-", spp, x2016, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
```

>>>>

---
title: "Plot `r paste(params$species)` responses to climate covariates to inform threshold choices for VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document
params: 
    #species: "Redbanded Rockfish"
    #species: "Pacific Ocean Perch"
    #species: "Pacific Cod"
    #species: "Petrale Sole" 
    species: "Arrowtooth Flounder" #"Curlfin Sole"
    priors: FALSE # call model that used priors?
    log_temp: TRUE # should temperature be log()
    model_w_do: TRUE
    # covs is a covariate string used to name model
    # if
    #fix_depth: FALSE 
    #covs: "-tv-depth-all-"
    #covs: "-tv-depth-past-2015" 
    # or if 
    fix_depth: TRUE
    covs: "-fixed-all-" 
    #covs: "-fixed-past-2017"
    cov_number: 2 
---

@@

try({
  # loads global models with 2016 excluded due to strangely high DO 
  add2016 <- ""
  x2016 <- "x2016"
  # for models using 2016 
  # add2016 <- "-do"
  #  x2016 <- ""
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  adult<-sdmTMB:::update_model(adult) 
  imm <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm <-sdmTMB:::update_model(imm) 
  })
  try({total <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, add2016, covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult")) adult <- NULL
if (!exists("imm")) imm <- NULL
if (!exists("total")) total <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey1 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey1 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  })
  try({total1 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
  })
if (!exists("adult_survey1")) adult_survey1 <- NULL
if (!exists("imm_survey1")) imm_survey1 <- NULL
if (!exists("total1")) total1 <- NULL

try({
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey4 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  imm_survey4 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
  })
  try({total4 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult_survey4")) adult_survey4 <- NULL
if (!exists("imm_survey4")) imm_survey4 <- NULL
if (!exists("total4")) total4 <- NULL

try({
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  try({adult_survey16 <- readRDS(paste0("data/", spp,
    "/mod-mat-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
   ))
   imm_survey16 <- readRDS(paste0("data/", spp,
    "/mod-imm-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"
   ))
  })
  try({total16 <- readRDS(paste0("data/", spp,
    "/model-total-biomass-", spp, covs, "-", ssid_string, "-prior-", priors, ".rds"))
  })
})
if (!exists("adult_survey16")) adult_survey16 <- NULL
if (!exists("imm_survey16")) imm_survey16 <- NULL
if (!exists("total16")) total16 <- NULL

@@

  if (length(do[[i]])>0) {
   do[[i]]$species <- species
   do[[i]]$age <- ifelse(grepl("imm", names(model_list[i])), "imm", "adult")
   do[[i]]$ssid <- paste0(sort(unique(as.numeric(model_list[[i]]$data$ssid))), collapse = "n")
   do[[i]]$model <- names(model_list[i])
   do[[i]]$covs <- paste0(x2016, covs, priors) 
   roots <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.5)
   do[[i]]$optimal_do <- exp(roots[["optimal"]])
   do[[i]]$lower_do_50 <- exp(roots[["lower_threshold"]])
   do[[i]]$upper_do_50 <- exp(roots[["upper_threshold"]])
   roots75 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.75)
   do[[i]]$lower_do_75 <- exp(roots75[["lower_threshold"]])
   do[[i]]$upper_do_75 <- exp(roots75[["upper_threshold"]])
   roots25 <- get_quadratic_roots(model_list[[i]], predictor = "do_mlpl", fixed_param = 1, threshold = 0.25)
   do[[i]]$lower_do_25 <- exp(roots25[["lower_threshold"]])
   do[[i]]$upper_do_25 <- exp(roots25[["upper_threshold"]])
   do[[i]]$x <- exp(do[[i]]$x)
   do_plots[[i]] <- 
     plot_mountains(do[[i]], variable_label = "Dissolved O2", xlimits = c(0.65, 6.25), x_breaks = c(1,2,3,4,5,6,7,8)) +
        ggtitle(paste(species, names(model_list[i]))) +
        geom_vline(xintercept=(do[[i]]$lower_do_50), linetype="longdash", alpha = 0.75) +
        #geom_vline(xintercept=(do[[i]]$upper_do_50), linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=(do[[i]]$lower_do_75), linetype="dotted", alpha = 0.5) +
        #geom_vline(xintercept=(do[[i]]$upper_do_75), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$lower_do_25), linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=(do[[i]]$optimal_do), size= 1.2, colour = "darkgrey") 
        #geom_vline(xintercept=(do[[i]]$upper_do_25), linetype="dotted", alpha = 0.5) 
   } else {
    do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
   }
 } else {
  do_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
 }
}

@@

   temp_plots[[i]] <- 
     plot_mountains(td[[i]], variable_label = "Temperature", xlimits = c(4.68, 9.93), x_breaks = c(3,4,5,6,7,8,9,10,11)) +
        ggtitle(paste(species, names(model_list[i]))) + 
        geom_vline(xintercept=td[[i]]$lower_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$upper_t_50, linetype="longdash", alpha = 0.75) +
        geom_vline(xintercept=td[[i]]$lower_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$upper_t_75, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$lower_t_25, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$upper_t_25, linetype="dotted", alpha = 0.5) +
        geom_vline(xintercept=td[[i]]$optimal_t, size= 1.2, colour = "darkgrey") 
  } else {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } 
 } else {
    temp_plots[[i]] <- grid::grid.rect(gp = grid::gpar(col = "white"))
  } 
}

@@

Save DO plots
```{r eval=T}
if(model_w_do) {
png(
  file = paste0("figs/", spp, "/do-", spp, x2016, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = do_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
}
```

Save temperature plots
```{r eval=T}
png(
  file = paste0("figs/", spp, "/temp-", spp, x2016, covs, "-priors-", priors, ".png"),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = temp_plots,
  nrow = 4,
  top = grid::textGrob(paste(species))
)
dev.off()
```
